Data Preparation, Integration and Cleaning

### 2018-05-04 scripts/3_data_prep.Rmd
Update:  filter function

---
title: "Data Preparation, Integration and Cleaning"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

@@

### Trim and Standardize Fields

The data contain many fields that are either not fully observed and/or are not relevant to our research question.  Additionally, the field naming conventions differ between the two datasets. We first remove unnecessary or unobserved fields and then employ a systematic field naming functions across all datasets.

We start by trimming the property-level short term data.  No fields need to be removed from the daily data.

While trimming the fields we also we standardize the field names.  Here we follow the convention of placing an underscore between words in the name.  We also shorten a number of the fields to make future coding easier.

```{r trim_st, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

   str_df <- str_df %>% 
     dplyr::select(property_id=property.id, host_id=host.id, listing_title=listing.title, 
                   property_type=property.type, listing_type=listing.type,
                   created_date=created.date, latitude, longitude, rating=overall.rating,
                   max_guests=max.guests, canc_policy=cancellation.policy, 
                   cleaning_fee=cleaning.fee, nightly_rate=published.nightly.rate, 
                   weekly_rate=published.weekly.rate, monthly_rate=published.monthly.rate, 
                   avg_nightly_rate=average.daily.rate, min_stay=minimum.stay, bedrooms, 
                   bathrooms, min_date=min.date, max_date=max.date, days=total.days, 
                   block_rate=block.rate, avail_rate=avail.rate, 
                   longest_block=longest.block, nbr_blocks=nbr.block, med_block=med.block,
                   created_year=created.year)

  daily_df <- daily_df %>%
    dplyr::select(property_id=property.id, date, status, price, booked_date=booked.date,
                  resv_id=reservation.id)

We then limit the fields of the long-term property-specific data

```{r trim_lt, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ltr_df <- ltr_df %>%
    dplyr::select(id_key=id.key, geo_id=geographicalid, event_id=eventid, 
                  addr_id=addressid, activity_id=activityid, flat_nbr=flatnumber,
                  str_nbr=streetnumber, str_name=streetname, str_type=streettype, 
                  suburb, postcode, latitude=property_latitude,
                  longitude=property_longitude, str_latitude=street_centroid_latitude,
                  str_longitude=street_centroid_longitude, event_date=event.date,
                  event_price=eventprice, property_type=propertytype, area_size=areasize,
                  bedrooms, baths, parking, has_study=hasstudy, 
                  has_courtyard=hascourtyard, has_balcony=hasbalcony, 
                  has_ac=hasairconditioning, has_garage=hasgarage, dom)

  list_df <- list_df %>%
    dplyr::select(id_key=id.key, event_id=eventid, activity_id=activityid, 
                  addr_id=addressid, of_record=of.record, event_date=event.date,
                  event_price=eventprice, first_date=first.adv.date, 
                  first_price=firstadvertisedeventprice, last_date=last.adv.date,
                  last_price=lastadvertisedeventprice, event_code=eventtypecode)

@@

  str_df <- str_df[(str_df$max_date - str_df$min_date) >= 178, ]
  str_df <- str_df[str_df$max_date >= (decision_date + 182) &
                    str_df$min_date <= (decision_date + 182), ]

  daily_df <- daily_df[daily_df$date >= decision_date, ]

  # Limit long term data

  ltr_df <- ltr_df[ltr_df$event_date >= (decision_date - 365) &
                    ltr_df$event_date <= (decision_date - 1), ]
  list_df <- list_df[list_df$id_key %in% ltr_df$id_key, ]

>>>>

---
title: "Data Preparation, Integration and Cleaning"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

@@

@@

  str_tdf <- str_tdf %>%
    dplyr::filter((max_date - min_date) >= 178) %>%
    dplyr::filter((max_date >= (decision_date + 182) &
                    min_date <= (decision_date + 182)))

  str_tdf <- str_tdf %>%
    tidyr::unnest() %>% 
    dplyr::filter(date >= decision_date) %>%
    tidyr::nest(date:uniq_id, .key=daily_data)

  # Limit long term data
  ltr_tdf <- ltr_tdf %>%
    dplyr::filter((event_date >= (decision_date - 365) &
                    event_date <= (decision_date - 1)))

  list_df <- list_df[list_df$id_key %in% ltr_df$id_key, ]
